Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model

### 2015-01-27 msc-publication.tex
add table of stats for advection

\documentclass[a4paper]{article}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{siunitx}

@@

@@

\section{Conclusions}
\begin{enumerate}
	\item BTF grid isn't as bad as people say it is.  We found that:
	\begin{itemize}
		\item Upwind-biased cubic advection scheme accurately advects a tracer in non-divergent flows (Figure~\ref{fig:advection})
		\item Advection in a TF velocity field, if we include it, gives better results on BTF than SnapCol (Figure~\ref{fig:wobblyTracerAdvection})
		\item spurious vertical velocities are small in resting atmosphere (Figure~\ref{fig:resting})  Could also compare with \textcite{zaengl2012}, \textcite{good2014}
		\item gravity waves results visually as good as reference solution from \textcite{melvin2010} (figure~\ref{fig:gw-w})
	\end{itemize}

@@

Miscellany:
\begin{itemize}
	\item Advection accuracy depends on alignment of the flow with grid layers
	\item Little/no evidence of small cell problem in GW test
	\item Lack of energy conservation (evidenced in resting atmosphere test, Fig 4.12d in MSc dissertation)
\end{itemize}

\section{Further work}
\begin{itemize}
	\item Lorenz computational mode motivates formulation of C-P staggering on unstructured grids
	\item Find out what excites the Lorenz computational mode
	\item Fix lack of energy conservation
\end{itemize}

>>>>

\documentclass[a4paper]{article}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{siunitx}
\usepackage{booktabs}

@@

\begin{table}
\centering
\begin{tabular}{ l l l l l l }
\toprule
& \multicolumn{3}{c}{Cubic upwind-biased} & \multicolumn{2}{c}{Sch\"ar 4th order} \\
& $\ell^2$ error & min & max & min & max \\
\midrule
Analytic  & 0 & 0 & 1 & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\
BTF 	  & TODO & TODO & TODO & \num{-0.058} & \num{1.001} \\
SnapCol   & TODO & TODO & TODO & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\
noOrography & TODO & TODO & TODO & \num{-0.002} & \num{0.984} \\
\bottomrule
\end{tabular}
%
\caption{Min, max and error norms compared with \textcite{schaer2002}}
\label{tab:advection-stats}
\end{table}

@@

\section{Conclusions}
\begin{enumerate}
	\item BTF grid isn't as bad as people say it is.  We found that:
	\begin{itemize}
		\item Upwind-biased cubic advection scheme accurately advects a tracer in non-divergent flows (Figure~\ref{fig:advection}, Table~\ref{tab:advection-stats})
		\item Advection in a TF velocity field, if we include it, gives better results on BTF than SnapCol (Figure~\ref{fig:wobblyTracerAdvection})
		\item spurious vertical velocities are small in resting atmosphere (Figure~\ref{fig:resting})  Could also compare with \textcite{zaengl2012}, \textcite{good2014}
		\item gravity waves results visually as good as reference solution from \textcite{melvin2010} (figure~\ref{fig:gw-w})
	\end{itemize}

@@

Miscellany:
\begin{itemize}
	\item Advection accuracy depends on alignment of the flow with grid layers
	\item Little/no evidence of small cell problem in GW test
	\item Formulation does not conserve energy (evidenced in resting atmosphere test, Fig 4.12d in MSc dissertation)
\end{itemize}

\section{Further work}
\begin{itemize}
	\item Lorenz computational mode motivates formulation of C-P staggering for cut cell grids
	\item Find out what excites the Lorenz computational mode
\end{itemize}
